### 2013-09-18 chi2014/conclusions.tex
fix quotations

We found that originality increased as brainstorming participants were asked to generate more ideas individually. Generality, however, decreased. In both cases, we found a "sweet spot" for this change at the 20 idea mark; participants' ideas reach their peak creativity and minimum generality after their 20th contribution.

>>>>

We found that originality increased as brainstorming participants were asked to generate more ideas individually. Generality, however, decreased. In both cases, we found a ``sweet spot" for this change at the 20 idea mark; participants' ideas reach their peak creativity and minimum generality after their 20th contribution.
